Stats

### 2022-02-23 paper/manuscript.tex
add the first plots for interind variation

Our newly implemented balloon finding task displays cartoon-like stimuli that are engaging for children and adults alike. An animal character (i.e., agent; sheep, monkey, or pig) is placed centrally in a window. A balloon (i.e., target; blue, green, yellow, or red) is located in front of them. The target then falls to the ground. At all times, the agent's gaze tracks the movement of the target. That is, the pupils and iris of the agent move in a way that their center aligns with the center of the target. While the distance of the target's flight depends on the final location, the target moves at a constant speed. Participants are then asked to locate the target's position on the screen.

@@

Before participants advance to the test trials, we present four training trials. In the first training trial, participants have full visual access to the target flight and the target's end location and are simply asked to click on the visible balloon. In the second and third training trials, participants have partial visual access: they witness the target flight but cannot see the target's end location. They are then asked to click on the invisible balloon, i.e., the location where they saw the target land. In test trials, participants have no visual access to the target flight nor the end location. Participants are expected to use the agent's gaze as a cue to locate the target. The first trial of each type comprises a voice-over description of the presented events. The audio descriptions explicitly state that the agent is always looking at the target (see Appendix for audio script). After these four training and audio guided trials, participants receive 15 test trials. The complete sequence of four training trials and 15 test trials can be administered within 5-10 minutes of testing time.

@@

Our balloon finding task is presented as an interactive web-app. The task is portable across devices and web browsers and does not require any installation. A great advantage of online testing is that our testing procedure is standardized across participants. By using pre-recorded study instructions,no interaction with the experimenter is necessary during the study. The code is open-source (\url{https://github.com/ccp-eva/gafo-demo}) and a live demo version can be found under: \url{https://ccp-odc.eva.mpg.de/gafo-demo/}.

@@

The web-app generates two file types: (1) a text file (.json) containing meta-data, trial specifications and participants' click responses, and (2) a video file (.webm) of the participant's webcam recording.
For our samples described in this paper, we deployed the web-app on servers located in Leipzig, Germany. Data got automatically collected and safely stored on these in-house servers. If no internet connection or server is available, researchers could download a local version of the experiment which stores the generated data automatically on the used device.

@@

\caption{\textbf{Infrastructure for online testing}. With our new infrastructure, subjects aged 3 -- 99+ can participate. Data collection is efficient and automatized and can take place anywhere: at home, in kindergartens or research institutes. Our task is presented as a website that works across devices. The scripts for the website and recorded data are stored on secure local servers.}\label{fig:fig2}
\end{figure}

@@

\begin{itemize}
\tightlist
\item
  workflow server to R, converting coordinate systems
  We used R {[}Version 4.1.2; R Core Team (2021){]} and the R-package \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]} for all our analyses.
  For child samples, we uploaded safety copies of the already collected responses after the fourth test trial. In cases where children want to stop participation earlier, no responses get lost. All test trials without voice over description are included in our analyses.
\end{itemize}

@@

Our first aim was to assess whether our balloon finding task induces variation in a child and adult sample. The pre-registrations can be found here: \url{https://osf.io/snju6} (child sample) and here: \url{https://osf.io/r3bhn} (adult sample). Participants were equally distributed across the two study versions.

@@

All participants received 15 test trials that were displayed as described above. In the box version, we decided to adjust the task difficulty according to the participant's age: children were presented with five boxes while adults were presented with eight boxes as possible hiding location of the target.

@@

@@

@@

@@

\hypertarget{discussion-1}{%
\section{Discussion}\label{discussion-1}}

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-R-papaja}{}}%
Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Create} {APA} manuscripts with {R Markdown}}. Retrieved from \url{https://github.com/crsh/papaja}

@@

>>>>

Our newly implemented balloon finding task displays cartoon-like stimuli that are engaging for children and adults alike. An animal character (i.e., agent; sheep, monkey, or pig) is placed centrally in a window. A balloon (i.e., target; blue, green, yellow, or red) is located in front of them. The target then falls to the ground. At all times, the agent's gaze tracks the movement of the target. That is, the pupils and iris of the agent move in a way that their center aligns with the center of the target. While the distance of the target's flight depends on the final location, the target moves at a constant speed. Participants are then asked to locate the target's destination: they respond by touching or clicking onto position on the screen.

@@

Before the test trials start, we present four training trials during which participants familiarize themselves with selection positions on the screen. In the first training trial, participants have full visual access to the target flight and the target's end location and are simply asked to click on the visible balloon. In the second and third training trials, participants have partial visual access: they witness the target flight but cannot see the target's end location. They are then asked to click on the invisible balloon, i.e., the location where they saw the target land. In test trials, participants have no visual access to the target flight nor the end location. Participants are expected to use the agent's gaze as a cue to locate the target. The first trial of each type comprises a voice-over description of the presented events. The audio descriptions explicitly state that the agent is always looking at the target (see Appendix for audio script). After these four training and audio guided trials, participants receive 15 test trials. The complete sequence of four training trials and 15 test trials can be administered within 5-10 minutes of testing time.

@@

Our balloon finding task is presented as an interactive web-app. The task is portable across devices and web browsers and does not require any installation. A great advantage of online testing is that our testing procedure is standardized across participants. By using pre-recorded study instructions, no interaction with the experimenter is necessary during the study. The code is open-source (\url{https://github.com/ccp-eva/gafo-demo}) and a live demo version can be found under: \url{https://ccp-odc.eva.mpg.de/gafo-demo/}.

@@

The web-app generates two file types: (1) a text file (.json) containing meta-data, trial specifications and participants' click responses, and (2) a video file (.webm) of the participant's webcam recording.
For our samples described in this paper, we deployed the web-app on servers located in Leipzig, Germany. Data got automatically collected and safely stored on these in-house servers. If no internet connection or server is available, researchers could download a local version of the experiment which stores the generated data automatically on the used device. For child samples, we upload safety copies of the already collected responses after the fourth test trial. In cases where children want to stop participation earlier, no responses get lost.

@@

\caption{\textbf{Infrastructure for online testing}. (i) With our new infrastructure, subjects aged 3 -- 99+ can participate. Data collection is efficient and automatized and can take place anywhere: at home, in kindergartens or research institutes. (ii) Our task is presented as a website that works across devices. (iii) The scripts for the website and recorded data are stored on secure local servers.}\label{fig:fig2}
\end{figure}

@@

We used R {[}Version 4.1.2; R Core Team (2021){]} and the R-packages \emph{brms} {[}Version 2.15.0; Bürkner (2017); Bürkner (2018){]}, \emph{dplyr} {[}Version 1.0.7; Wickham, François, Henry, and Müller (2021){]}, \emph{forcats} {[}Version 0.5.1; Wickham (2021a){]}, \emph{ggplot2} {[}Version 3.3.5; Wickham (2016){]}, \emph{ggpubr} {[}Version 0.4.0; Kassambara (2020){]}, \emph{ggthemes} {[}Version 4.2.4; Arnold (2021){]}, \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]}, \emph{purrr} {[}Version 0.3.4; Henry and Wickham (2020){]}, \emph{Rcpp} {[}Version 1.0.6; Eddelbuettel and François (2011); Eddelbuettel and Balamuta (2018){]}, \emph{readr} {[}Version 1.4.0; Wickham and Hester (2020){]}, \emph{stringr} {[}Version 1.4.0; Wickham (2019){]}, \emph{tibble} {[}Version 3.1.6; Müller and Wickham (2021){]}, \emph{tidyboot} {[}Version 0.1.1; Braginsky and Yurovsky (2018){]}, \emph{tidyr} {[}Version 1.1.4; Wickham (2021b){]}, \emph{tidyverse} {[}Version 1.3.1; Wickham et al. (2019){]}, \emph{viridis} {[}Version 0.6.1; Garnier et al. (2021a); Garnier et al. (2021b){]}, and \emph{viridisLite} {[}Version 0.4.0; Garnier et al. (2021b){]} for all our analyses. Regression models were fitted as Bayesian generalized linear mixed models (GLMMs) with default priors for all analyses.
All test trials without voice over description are included in our analyses.

@@

Our first aim was to assess whether our balloon finding task induces variation in a child and adult sample. The pre-registrations can be found here: \url{https://osf.io/snju6} (child sample) and here: \url{https://osf.io/r3bhn} (adult sample). Participants were equally distributed across the two study versions. The study was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology. Data was collected between May 2021 and XXX 2022.

@@

Children were tested in a quiet room in their daycare. An experimenter guided the child through the different parts of the study.
All participants received 15 test trials that were displayed as described above. In the box version, we decided to adjust the task difficulty according to the participant's age: children were presented with five boxes while adults were presented with eight boxes as possible hiding location of the target.

@@

\begin{itemize}
\tightlist
\item
  sanity check: developmental trajectory
\item
  remote testing: online child sample as side note
\end{itemize}

We captured a developmental trajectory of gaze cue understanding. With increasing age, participants get more and more accurate in their performance.

\begin{figure}
\includegraphics[width=0.49\linewidth]{../figures/gafo_hedge_variation} \includegraphics[width=0.49\linewidth]{../figures/gafo_box_variation} \caption{\textbf{Interindividual variation}.
The regression line shows the developmental trajectory (with 95\% CI) of children's performance by age.
Colored diamonds show means by age in years (with 95\% CI based on non-parametric bootstrap). Light shapes show the mean performance for each subject.
(a) Variation in the hedge version. Here, we measure performance as the average imprecision, i.e., the absolute click distance between the target's center and the participant's click. The unit of imprecision is counted in the width of the target, i.e., a participant with an imprecision of 1 clicked in average one target width to the left or right of the true target center.
(b) Variation in the box version. Performance is measured as the proportion of correct responses, i.e., how many times the participant clicked on the box that actually contained the target. The straight line shows level of performance expected by chance for the child sample (20\%, i.e., 1 out of 5 boxes). Dotted line shows level of performance expected by chance for the adult sample (12.5\%, i.e., 1 out of 8 boxes).}\label{fig:fig3}
\end{figure}

TODO: For investigating the internal consistency of our task, we split the test trials into halves\ldots{}

@@

\hypertarget{discussion-1}{%
\subsection{Discussion}\label{discussion-1}}

Study 1 showed that our newly implemented balloon finding task can be used to study gaze cue understanding in both children and adults. With increasing age, participants got more and more precise in locating the target. We found inter-individual variation in across all age groups: some three-year-olds were more precise than some five-year-olds. Internal consistency indicated that the measured variation was systematic. These results hold for both the continuous hedge version as well as the discrete box version of the task. Furthermore, we found comparable results for an unsupervised remote child sample. This underlines how flexibly our new task can be used.

@@

Based on the results of Study 1, we wanted to further investigate the reliability of our measure. We analyzed the test-retest reliability by testing the same individual twice.

@@

\hypertarget{discussion-2}{%
\section{Discussion}\label{discussion-2}}

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-R-ggthemes}{}}%
Arnold, J. B. (2021). \emph{Ggthemes: Extra themes, scales and geoms for 'ggplot2'}. Retrieved from \url{https://CRAN.R-project.org/package=ggthemes}

\leavevmode\vadjust pre{\hypertarget{ref-R-papaja}{}}%
Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Create} {APA} manuscripts with {R Markdown}}. Retrieved from \url{https://github.com/crsh/papaja}

\leavevmode\vadjust pre{\hypertarget{ref-R-tidyboot}{}}%
Braginsky, M., \& Yurovsky, D. (2018). \emph{Tidyboot: Tidyverse-compatible bootstrapping}. Retrieved from \url{https://CRAN.R-project.org/package=tidyboot}

\leavevmode\vadjust pre{\hypertarget{ref-R-brms_a}{}}%
Bürkner, P.-C. (2017). {brms}: An {R} package for {Bayesian} multilevel models using {Stan}. \emph{Journal of Statistical Software}, \emph{80}(1), 1--28. \url{https://doi.org/10.18637/jss.v080.i01}

\leavevmode\vadjust pre{\hypertarget{ref-R-brms_b}{}}%
Bürkner, P.-C. (2018). Advanced {Bayesian} multilevel modeling with the {R} package {brms}. \emph{The R Journal}, \emph{10}(1), 395--411. \url{https://doi.org/10.32614/RJ-2018-017}

\leavevmode\vadjust pre{\hypertarget{ref-R-Rcpp_b}{}}%
Eddelbuettel, D., \& Balamuta, J. J. (2018). {Extending extit{R} with extit{C++}: A Brief Introduction to extit{Rcpp}}. \emph{The American Statistician}, \emph{72}(1), 28--36. \url{https://doi.org/10.1080/00031305.2017.1375990}

\leavevmode\vadjust pre{\hypertarget{ref-R-Rcpp_a}{}}%
Eddelbuettel, D., \& François, R. (2011). {Rcpp}: Seamless {R} and {C++} integration. \emph{Journal of Statistical Software}, \emph{40}(8), 1--18. \url{https://doi.org/10.18637/jss.v040.i08}

\leavevmode\vadjust pre{\hypertarget{ref-R-viridis}{}}%
Garnier, Simon, Ross, Noam, Rudis, Robert, \ldots{} Cédric. (2021a). \emph{{viridis} - colorblind-friendly color maps for r}. \url{https://doi.org/10.5281/zenodo.4679424}

\leavevmode\vadjust pre{\hypertarget{ref-R-viridisLite}{}}%
Garnier, Simon, Ross, Noam, Rudis, Robert, \ldots{} Cédric. (2021b). \emph{{viridis} - colorblind-friendly color maps for r}. \url{https://doi.org/10.5281/zenodo.4679424}

\leavevmode\vadjust pre{\hypertarget{ref-R-purrr}{}}%
Henry, L., \& Wickham, H. (2020). \emph{Purrr: Functional programming tools}. Retrieved from \url{https://CRAN.R-project.org/package=purrr}

\leavevmode\vadjust pre{\hypertarget{ref-R-ggpubr}{}}%
Kassambara, A. (2020). \emph{Ggpubr: 'ggplot2' based publication ready plots}. Retrieved from \url{https://CRAN.R-project.org/package=ggpubr}

\leavevmode\vadjust pre{\hypertarget{ref-R-tibble}{}}%
Müller, K., \& Wickham, H. (2021). \emph{Tibble: Simple data frames}. Retrieved from \url{https://CRAN.R-project.org/package=tibble}

@@

\leavevmode\vadjust pre{\hypertarget{ref-R-ggplot2}{}}%
Wickham, H. (2016). \emph{ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}

\leavevmode\vadjust pre{\hypertarget{ref-R-stringr}{}}%
Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for common string operations}. Retrieved from \url{https://CRAN.R-project.org/package=stringr}

\leavevmode\vadjust pre{\hypertarget{ref-R-forcats}{}}%
Wickham, H. (2021a). \emph{Forcats: Tools for working with categorical variables (factors)}. Retrieved from \url{https://CRAN.R-project.org/package=forcats}

\leavevmode\vadjust pre{\hypertarget{ref-R-tidyr}{}}%
Wickham, H. (2021b). \emph{Tidyr: Tidy messy data}. Retrieved from \url{https://CRAN.R-project.org/package=tidyr}

\leavevmode\vadjust pre{\hypertarget{ref-R-tidyverse}{}}%
Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L. D., François, R., \ldots{} Yutani, H. (2019). Welcome to the {tidyverse}. \emph{Journal of Open Source Software}, \emph{4}(43), 1686. \url{https://doi.org/10.21105/joss.01686}

\leavevmode\vadjust pre{\hypertarget{ref-R-dplyr}{}}%
Wickham, H., François, R., Henry, L., \& Müller, K. (2021). \emph{Dplyr: A grammar of data manipulation}. Retrieved from \url{https://CRAN.R-project.org/package=dplyr}

\leavevmode\vadjust pre{\hypertarget{ref-R-readr}{}}%
Wickham, H., \& Hester, J. (2020). \emph{Readr: Read rectangular text data}. Retrieved from \url{https://CRAN.R-project.org/package=readr}

### 2022-02-23 stats/analysis.Rmd
add some more setup stuff
add the first plots for interind variation

---
title: "Measuring individual differences in the understanding of gaze cues"
author: "Julia Prein"
date: "12/17/2021"
output: pdf_document
---

@@

# Introduction

# Methods
## Participants
## Procedure
## Data analysis

# Results

# Discussion

# References

# Acknowledgements

# Author Contributions

>>>>

---
title: "Stats"
author: "Julia Prein"
date: "12/17/2021"
output: pdf_document
---

@@

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(viridis) # color scales
library(ggpubr)
library(tidyboot)
library(ggthemes)
library(brms)

options(scipen = 999)
theme_set(theme_classic())
```

```{r load_data}
testtrials <- readRDS(file = "../data/gafo-testtrials.rds") %>% 
  # determine order of factors
  mutate(
    targetPosition = factor(targetPosition, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "box1", "box2", "box3", "box4", "box5")), 
    studyversion = factor(studyversion, levels = c("hedge", "box")), 
    datacollection = factor(datacollection, levels = c("in-person - supervised", "remote - unsupervised")),
    sample = factor(sample, levels = c("kids", "adults")), 
    studytype = factor(studytype, levels = c("vali", "vali2", "reli"))
  )
```

```{r vali_data}
vali <- testtrials %>% 
  filter(studytype == "vali" & (ageInYears < 6 | ageInYears == 18))
```

```{r}
variationHedgeKids <- vali %>% 
  filter(studyversion == "hedge" & sample == "kids" & datacollection == "in-person - supervised") %>% 
  group_by(ageInYears, ageInMonths, subjID) %>%
  tidyboot_mean(col = abs(clickDistFromTargetCenterX), na.rm = TRUE) %>% 
  group_by(ageInYears) %>% 
  arrange(desc(mean), .by_group = TRUE) %>% 
  mutate(
    subjID = as_factor(subjID), 
    ageInYears = as_factor(ageInYears)
  )

variationHedgeAdultsInd <- vali %>% 
  filter(sample == "adults" & studyversion == "hedge") %>% 
  group_by(ageInYears, subjID) %>%
  tidyboot_mean(col = abs(clickDistFromTargetCenterX), na.rm = TRUE)

variationHedgeAdults <- vali %>% 
  filter(sample == "adults" & studyversion == "hedge") %>% 
  tidyboot_mean(col = abs(clickDistFromTargetCenterX), na.rm = TRUE)

ggplot(data = variationHedgeKids, aes(x = ageInMonths, y = mean/160)) +
  geom_pointrange(aes(ymin = ci_lower/160, ymax = ci_upper/160), position = position_jitter(width = 0.5), size = .25, colour = "darkgrey") +
  geom_smooth(method = "glm", color = "#006c66", alpha = 0.2) +
  labs(x = "Age in months", y = "Average imprecision in target width") + 
  geom_point(data = variationHedgeAdults, aes(x = 78, y = mean/160), color = "#006c66", size = 1) + 
  scale_y_continuous(limits = c(0, 6), breaks = seq(0, 6, 1)) +
  geom_errorbar(data = variationHedgeAdults, aes(x = 78, ymin = ci_lower/160, ymax = ci_upper/160), width = 0.2, color = "#006c66") +
  scale_x_continuous(breaks = seq(36, 78, 6), labels = c(paste0(seq(36, 72, 6)), expression(paste("Adults ",italic("(N"), "= 50)"))))

ggsave("../figures/gafo_hedge_variationAgeMonths.png", width = 6, height = 4)
```

```{r}
vali %>% 
  filter(studyversion == "hedge" & ((sample == "kids" & datacollection == "in-person - supervised") | sample == "adults")) %>% 
  group_by(ageInYears) %>% 
  summarise(n = n_distinct(subjID))

variationHedgeAgegroups <- vali %>% 
  filter(studyversion == "hedge" & ((sample == "kids" & datacollection == "in-person - supervised") | sample == "adults")) %>% 
  group_by(ageInYears) %>%
  tidyboot_mean(col = abs(clickDistFromTargetCenterX), na.rm = TRUE)

variationHedgeAgegroupsInd <- vali %>% 
  filter(studyversion == "hedge" & ((sample == "kids" & datacollection == "in-person - supervised") | sample == "adults")) %>% 
  group_by(ageInYears, subjID) %>%
  tidyboot_mean(col = abs(clickDistFromTargetCenterX), na.rm = TRUE)

ggplot() +
  geom_jitter(data = variationHedgeAgegroupsInd, aes(x = as.factor(ageInYears), y = mean/160), alpha = .8, width = 0.1, height = 0, col = "grey") + 
  geom_pointrange(data = variationHedgeAgegroups, aes(x = as.factor(ageInYears), y = mean/160, ymin = ci_lower/160, ymax = ci_upper/160), 
    size = 0.8, pch = 18) +
  labs(x = "Age", y = "Average imprecision in target width") + 
  scale_y_continuous(limits = c(0, 5), breaks = seq(0, 5, 1)) +
  scale_x_discrete(breaks = c(3, 4, 5, 18), labels = c(expression(paste("3-year-olds ",italic("(N"), "= 20)")), expression(paste("4-year-olds ",italic("(N"), "= 20)")), expression(paste("5-year-olds ",italic("(N"), "= 20)")), expression(paste("Adults ",italic("(N"), "= 50)"))))

ggsave("../figures/gafo_hedge_variationAgegroup.png", width = 6, height = 4)
```

```{r variation_hedge}
variationHedgeInd <- vali %>% 
  filter(studyversion == "hedge" & ((sample == "kids" & datacollection == "in-person - supervised") | sample == "adults")) %>% 
  mutate(
    ageInYearsExact = ageInMonths/12
  ) %>% 
  group_by(sample, ageInYears, ageInYearsExact, subjID) %>% 
  summarise(mean = mean(abs(clickDistFromTargetCenterX)/160, na.rm = TRUE))

variationHedge <- variationHedgeInd %>%
  group_by(sample, ageInYears) %>%
  tidyboot_mean(column = mean)

## without color
# ggplot() +
#   # child data
#   geom_smooth(data = variationHedgeInd %>% filter(sample == "kids"),  aes(x = ageInYearsExact, y = mean), method = "glm", color = "#006c66", alpha = 0.2) +
#   geom_point(data = variationHedgeInd %>% filter(sample == "kids"), aes(x = ageInYearsExact, y = mean), alpha = .25) +
#   geom_pointrange(data = variationHedge %>% filter(sample == "kids"), aes(x = as.numeric(as.character(ageInYears))+.5, y = mean, ymin = ci_lower, ymax = ci_upper), size = 0.8, pch = 18) + 
# 
#   # adult data
#   geom_jitter(data = variationHedgeInd %>% filter(sample == "adults"), aes(x = 6.5, y = mean), alpha = .15, width = .05, height = .01) +
#   geom_pointrange(data = variationHedge %>% filter(sample == "adults"), aes(x = 6.5, y = mean, ymin = ci_lower, ymax = ci_upper), size = 0.8, pch = 18) +  
#   labs(x = "Age in years", y = "Average imprecision in target width") + 
#   scale_y_continuous(limits = c(0, 5), breaks = seq(0, 5, 1)) +
#   scale_x_continuous(breaks = c(3.5, 4.5, 5.5, 6.5), labels = c(expression(paste("3-year-olds ",italic("(n"), "= 20)")), expression(paste("4-year-olds ",italic("(n"), "= 20)")), expression(paste("5-year-olds ",italic("(n"), "= 20)")), expression(paste("Adults ",italic("(n"), "= 50)"))))

## with color
ggplot() +
  # child data
  geom_smooth(data = variationHedgeInd %>% filter(sample == "kids"),  aes(x = ageInYearsExact, y = mean), method = "glm", color = "darkgrey", alpha = 0.2) +
  geom_point(data = variationHedgeInd %>% filter(sample == "kids"), aes(x = ageInYearsExact, y = mean, col = as.factor(ageInYears)), alpha = .5) +
  geom_pointrange(data = variationHedge %>% filter(sample == "kids"), aes(x = as.numeric(as.character(ageInYears))+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = as.factor(ageInYears)), size = 0.8, pch = 18) + 
  scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d"), labels = c("3-year-olds", "4-year-olds", "5-year-olds")) +

  # adult data
  geom_jitter(data = variationHedgeInd %>% filter(sample == "adults"), aes(x = 6.5, y = mean), alpha = .15, width = .05, height = .01) +
  geom_pointrange(data = variationHedge %>% filter(sample == "adults"), aes(x = 6.5, y = mean, ymin = ci_lower, ymax = ci_upper), size = 0.8, pch = 18) +  
  labs(x = "Age in years", y = "Average imprecision in target width", color = "Age group") + 
  scale_y_continuous(limits = c(0, 5), breaks = seq(0, 5, 1)) + 
  scale_x_continuous(breaks = seq(3, 6.5, 0.5), labels = c("3.0", "3.5", "4.0", "4.5", "5.0", "5.5", "6.0", "Adults")) + 
  theme(legend.position = c(0.11, 0.18))

ggsave("../figures/gafo_hedge_variation.png", width = 6, height = 4)
```

```{r variation_box}
variationBoxInd <- vali %>% 
  filter(studyversion == "box" & ((sample == "kids" & datacollection == "in-person - supervised") | sample == "adults")) %>% 
  mutate(
    ageInYearsExact = ageInMonths/12
  ) %>% 
  group_by(sample, ageInYears, ageInYearsExact, subjID) %>% 
  summarise(mean = mean(correctBox, na.rm = TRUE))

variationBox <- variationBoxInd %>%
  group_by(sample, ageInYears) %>%
  tidyboot_mean(column = mean)

ggplot() +
  # chance level
  geom_hline(aes(yintercept = 0.2), lty = 1) + 
  geom_hline(aes(yintercept = 0.125), lty = 2) +

  # child data
  geom_smooth(data = variationBoxInd %>% filter(sample == "kids"),  aes(x = ageInYearsExact, y = mean), method = "glm", color = "darkgrey", alpha = 0.2) +
  geom_point(data = variationBoxInd %>% filter(sample == "kids"), aes(x = ageInYearsExact, y = mean, col = as.factor(ageInYears)), alpha = .5) +
  geom_pointrange(data = variationBox %>% filter(sample == "kids"), aes(x = as.numeric(as.character(ageInYears))+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = as.factor(ageInYears)), size = 0.8, pch = 18) + 
  scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d"), labels = c("3-year-olds", "4-year-olds", "5-year-olds")) +

  # adult data
  geom_jitter(data = variationBoxInd %>% filter(sample == "adults"), aes(x = 6.5, y = mean), alpha = .15, width = .05, height = .01) +
  geom_pointrange(data = variationBox %>% filter(sample == "adults"), aes(x = 6.5, y = mean, ymin = ci_lower, ymax = ci_upper), size = 0.8, pch = 18) +  
  labs(x = "Age in years", y = "Proportion correct", color = "Age group") + 
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) + 
  scale_x_continuous(breaks = seq(3, 6.5, 0.5), labels = c("3.0", "3.5", "4.0", "4.5", "5.0", "5.5", "6.0", "Adults")) + 
  theme(legend.position = c(0.11, 0.85))

ggsave("../figures/gafo_box_variation.png", width = 6, height = 4)
```
